Investigate poor coverage for ash.hu

### 2017-01-03 analysis/investigate_hu_badcoverage.Rmd
Added chunk descriptions and succesfully rendered investigate_hu_badcoverage.Rmd after fixing problems with code in /output.

```{r chunk_options, include=FALSE}
library(ashr)
library(reshape2)
library(ggplot2)
library(dplyr)
source("chunk-options.R")
```

```{r}
load("../output/dsc-shrink-files/res.RData")

out <- res$negprob
neglong = 
  out %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars=c("method","scenario","seed",".id"),value.name = "negprob") %>%
    filter(negprob > 0.95)

poslong = 
  res$posprob %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars = c("method","scenario","seed",".id"),value.name="posprob") %>%
    filter(posprob > 0.95)

@@

```

```{r}
ash.hu.ft = reslong.pos %>% dplyr::filter(method=="ash.hu.s" & scenario=="flat-top")
head(ash.hu.ft)
```

```{r}
  eg=load_example(dsc_shrink,42,"flat-top",method="ash.hu.s","../code/dsc-shrink")
  eg$output$fitted_g
```

Notice how almost all the inferred weight is on a small positive component. As a result false sign rate will be small, and there will be a strong tendency
to overestimate 0 effects. This leads to coverage problems observed.

Now let's look at an example with u and spiky which seems to be somewhat badly calibrated for the negative discoveries. 
```{r}
ash.u.s.spiky = reslong.neg %>% dplyr::filter(method=="ash.u.s" & scenario=="spiky")
ash.n.s.spiky = reslong.neg %>% dplyr::filter(method=="ash.n.s" & scenario=="spiky")
hist(ash.u.s.spiky$value,nclass=100,main="histogram of quantile where observation falls in its CI; significant negative discoveries")
hist(ash.n.s.spiky$value,nclass=100,main="histogram of quantile where observation falls in its CI; significant negative discoveries")
```

@@

Can we find an example?
```{r}
  table((ash.u.s.spiky %>% filter(value==0))$seed)
  eg =load_example(dsc_shrink,seed = 39,method="ash.u.s",scenario="spiky","../code/dsc-shrink")
```

For comparison, here are the positive discoveries; here there is not too bad.
```{r}
ash.u.s.spiky = reslong.pos %>% dplyr::filter(method=="ash.u.s" & scenario=="spiky")
ash.n.s.spiky = reslong.pos %>% dplyr::filter(method=="ash.n.s" & scenario=="spiky")
hist(ash.n.s.spiky$value)
hist(ash.u.s.spiky$value)
```

>>>>

```{r chunk_options, include=FALSE}
library(ashr)
library(reshape2)
library(ggplot2)
library(dplyr)
library(dscr)
source("chunk-options.R")
```

Compile the tables which we will use to examine the results of the simulation
experiments.

```{r compile_tables}
load("../output/dsc-shrink-files/res.RData")

neglong = 
  res$negprob %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars = c("method","scenario","seed",".id"),value.name = "negprob") %>%
    filter(negprob > 0.95)

poslong = 
  res$posprob %>% 
    select(-user.self,-sys.self,-elapsed,-user.child,-sys.child) %>%
    melt(id.vars = c("method","scenario","seed",".id"),value.name = "posprob") %>%
    filter(posprob > 0.95)

@@

ash.hu.ft = reslong.pos %>% filter(method == "ash.hu.s" & 
                                   scenario == "flat-top")
```

Extract an example to illustrate coverage of ash.hu.

```{r show_example}
eg = load_example(dsc_shrink,42,"flat-top",methodname = "ash.hu.s",
                  homedir = "../code/dsc-shrink")
out        <- eg$output$fitted_g
class(out) <- "list"
out        <- as.data.frame(out)
print(subset(out,pi > 0.01))
```

Notice how almost all the inferred weight is on a small positive component. 
As a result, false sign rate will be small, and there will be a strong tendency
to overestimate zero effects. This leads to coverage problems observed.

Now let's look at an example with u and spiky which seems to be somewhat 
badly calibrated for the negative discoveries.

```{r show_more_examples}
ash.u.s.spiky = reslong.neg %>% filter(method == "ash.u.s" & 
                                       scenario == "spiky")
ash.n.s.spiky = reslong.neg %>% filter(method == "ash.n.s" & 
                                         scenario == "spiky")
hist(ash.u.s.spiky$value,nclass = 100,
     main = paste("histogram of quantile where observation falls in its CI"))
hist(ash.n.s.spiky$value,nclass = 100,
     main = paste("histogram of quantile where observation falls in its CI"))
```

@@

Can we find an example illustrating this trend? (Note: the next chunk below
did not work for me, so I se* `eval=FALSE, include=FALSE`. Perhaps this can be 
fixed at some point. -Peter)

```{r example_short_tail, eval=FALSE, include=FALSE}
table((ash.u.s.spiky %>% filter(value == 0))$seed)
eg = load_example(dsc_shrink,seed = 39,scenario = "spiky",
                  methodname = "ash.u.s","../code/dsc-shrink")
```

For comparison, here are the positive discoveries; here they are not too bad.

```{r histograms_pos}
ash.u.s.spiky = reslong.pos %>% filter(method == "ash.u.s" & scenario == "spiky")
ash.n.s.spiky = reslong.pos %>% filter(method == "ash.n.s" & scenario == "spiky")
hist(ash.n.s.spiky$value)
hist(ash.u.s.spiky$value)
```
